### 2015-04-28 inst/examples/synchrony-example.Rmd
adds plotting of per capita growth rates

The `get_community_synchrony` function requires several other packages...
```{r load_libs, echo=TRUE}
library(communitySynchrony)
library(plyr)
library(reshape2)
library(synchrony)
```

@@

>>>>

The `get_community_synchrony` function requires several other packages...
```{r load_libs, echo=TRUE}
library(communitySynchrony)
library(plyr)
library(reshape2)
library(synchrony)
library(ggplot2)
```

@@

### Plot per capita growth rates
```{r plotit, echo=TRUE, include=TRUE}
pgr_data <- out$growth_rates
pgr_melt <- melt(pgr_data, id.vars = "year")
ggplot(pgr_melt, aes(x=(year+1900), y=value, color=variable))+
  geom_line()+
  geom_point()
```
